Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-05-12 paper.tex
let's take a look to the SoA

  %[Pedro] otro caso muy similar es el paper de ChingChin2010 sobre:
  % New tea product
  % New cosmetic product
  % New soft drink product
In \cite{ChingChin2010}, a decision-support system for new product sales %FERGU: The work of Chinchin et al.?
forecasting is proposed to solve three real-world sales forecasting problems, namely: new tea, cosmetics, and soft drink products. This is addressed taking into account quantitative variables.
% Antonio - qué significa eso?
In that study, products are classified based on their sales patterns, so it is assumed that products in the same class would follow a similar sales pattern. 
However, as the authors state, the proposed system can not deal with qualitative 
data related to the products. Moreover, real-world cases, such as consumer 
electronics and fashion products, should be deeply analysed, as these industries 
present/launch new products every season.

>>>>

  %[Pedro] otro caso muy similar es el paper de ChingChin2010 sobre:
  % New tea product
  % New cosmetic product
  % New soft drink product
Ching et al. propose in \cite{ChingChin2010} a decision-support system for new product sales
forecasting is proposed to solve three real-world sales forecasting problems, namely: new tea, cosmetics, and soft drink products. This is addressed taking into account quantitative variables.
% Antonio - qué significa eso?
In that study, products are classified based on their sales patterns, so it is assumed that products in the same class would follow a similar sales pattern. 
However, as the authors state, the proposed system can not deal with qualitative 
data related to the products. Moreover, real-world cases, such as consumer 
electronics and fashion products, should be deeply analysed, as these industries 
present/launch new products every season.
